\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Commented out the section on 'Object Position Hypotheses' as it was never really properly finished

\paragraph{Hypotheses on Objects States and Positions}

Occlusions, be they purposeful (when an agent hides an object behind or inside
another one) or not, commonly lead to difficulties in perceiving and tracking
objects in certain states. To mitigate this issue, {\sc Spark} also models the
possible symbolic states of objects (whether the object is on a furniture, in an
agent hand, in a container, etc.) with an associated probability distribution
based on the robot's perception of what has happened since the object was last
seen.  This probabilistic model of the environment is not currently integrated
with the knowledge base, and is instead directly queried by the execution
controllers when necessary.

>>>>

%\paragraph{Hypotheses on Objects States and Positions}
%
%Occlusions, be they purposeful (when an agent hides an object behind or inside
%another one) or not, commonly lead to difficulties in perceiving and tracking
%objects in certain states. To mitigate this issue, {\sc Spark} also models the
%possible symbolic states of objects (whether the object is on a furniture, in an
%agent hand, in a container, etc.) with an associated probability distribution
%based on the robot's perception of what has happened since the object was last
%seen.  This probabilistic model of the environment is not currently integrated
%with the knowledge base, and is instead directly queried by the execution
%controllers when necessary.
